---
font: Lato
fontsize: 10pt
geometry: left=1in,right=1in,top=0.35in,bottom=0.6in
header-includes: \input{preamble.tex}
output:
  pdf_document: default
  word_document: default
sansfont: Lato
urlcolor: null
---

\raggedright

```{r rmarkdown-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

library(tidyverse)
library(knitr)
library(kableExtra)
library(dplyr)
library(scales)
library(arrow)
```

\clatitle{This is the title}
\clasubtitle{This is the subtitle}
\claauthors{Author1, Author2}

```{r import-data, echo=FALSE}
us_county<-arrow::read_parquet("../data/us-county-time-series.parquet", as_tibble=TRUE)
ca_hospitalizations<-read.csv("https://raw.githubusercontent.com/CityOfLosAngeles/covid19-indicators/master/data/ca-hospital-and-surge-capacity.csv")

# Call parameters from our utils files
source("../notebooks/r_utils.R")
YESTERDAY_DATE <-YESTERDAY_DATE
TWO_WEEKS_AGO <- TWO_WEEKS_AGO


# Call parameters from utils files
source("../notebooks/r_chart_utils.R")
# Chart parameters
NAVY<-NAVY
MAROON<- MAROON
LIGHT_GRAY<-LIGHT_GRAY
```


# Executive Summary

Here's what this report is about.

With some bullet points:

* One
* Two
* Three


Then some numbers:

1. **Important finding 1**: one
1. **Important finding 2**: two
1. **Important finding 3**: three

\contactinfo{}
\newpage{}


# Background

**bold** or *italic* or just regular words


# Methodology

Stuff

## Data Sources

Here's our data sources, let's add a table with some formatting!

\clatablenumber{1} 
\clatabletitle{Data Sources}
```{r data-sources, echo=FALSE}
# Insert table for data sources

text_table <- data.frame(
  Data = c("Dataset1",
           "Dataset2",
           "Dataset3"
           ),
  Source = c(
    "Source1",
    "Source2",
    "Source3" 
  ), 
  Years = c(
    "2000-2020", 
    "2000-2020",
    "2000-2020"
  )
)

kbl(text_table) %>%
  kable_material(full_width = F) %>%
  column_spec(1, width="5cm") %>%
  column_spec(2, width = "4.5cm") %>%
  column_spec(3, width = "1.75cm") %>%
  kable_styling(fixed_thead=T, position="left")
```
\clasource{Census Bureau}


# Analysis Findings



# Conclusion






